Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-04 papers/BON_VHDL/paper.tex
added Scalar types
added types

The \arch body represents description of the internal implementation 
of an \ent including only process statements, which are collections 
of actions to be executed in sequence, or simultaneous statements, 
which describe equations of analogue system behaviour. 
The textual presentation of \arch is shown in Figure.2.
\input{adc-arch}

@@

%======================================================================
\appendix
\section {APPENDIX}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
%\todo{dragan 27/07/2009 - Figure out :  VHDL-ASM as BON  represents an strongly typed language.}
\input{operators}
%======================================================================

>>>>

The \arch body represents description of the internal implementation 
of an \ent including only process statements(encapsulation), which are collections 
of actions to be executed in sequence, or simultaneous statements, 
which describe equations of analogue system behaviour. 
The textual presentation of \arch is shown in Figure.2.
\input{adc-arch}

@@

%======================================================================
\appendix
\section {APPENDIX}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
%\todo{dragan 27/07/2009 - Figure out :  static types.}
\input{operators}
%\todo{dragan 27/07/2009 - Figure out :  types/subtypes.}
\input{types}
%======================================================================
